Spatio-temporal estimates of HIV risk group proportions for adolescent girls and young women across 13 priority countries in sub-Saharan Africa

### 2022-06-10 src/docs_paper/paper.Rmd
Add two plots to paper.Rmd #128

@@

@@

@@

# Tables

# Figures

>>>>

<!-- \begin{table}[htb] -->
<!-- \small -->
<!-- \centering -->
<!-- \begin{tabularx}{\textwidth}{llX} -->
<!-- \toprule -->
<!-- Risk group & Description & Risk ratio \\  -->
<!-- \midrule -->
<!-- None & Not sexually active & 0 (Excludes incidence from non-sexual transmission, e.g. unsafe injection, which is negligible in these populations.) \\ -->
<!-- Low & One cohabiting sexual partner & 1 (Baseline group.) \\ -->
<!-- High & Non-regular sexual partner(s) & 1.72 (Based upon analyses of risk factors for incident HIV infection from studies in sub-Saharan Africa by \citet{slaymaker2020croi} and \citet{jia2022risk}.) \\ -->
<!-- Very high & Female sex workers & { -->
<!-- \begin{tabularx}{\cellwidth}{ll} -->
<!-- \hline -->
<!-- District-level HIV incidence & Risk ratio \Top{}\\ -->
<!-- $>$3.0\% & 3 \\ -->
<!-- 1.0-3.0\% & 6 \\ -->
<!-- 0.3-1.0\% & 9 \\ -->
<!-- 0.1-0.3\% & 13 \\ -->
<!-- $<$0.1\% & 25 \Bot{}\\ -->
<!-- \hline -->
<!-- \end{tabularx} -->
<!-- }\\ -->
<!-- \bottomrule -->
<!-- \end{tabularx} -->
<!-- \caption{HIV risk groups and risk ratios giving the ratio of probabilities of being sexually infected with HIV in the next year relative to the baseline group. Risk ratios for the highest risk group vary based upon general population HIV incidence and are based upon a UNAIDS analysis led by Keith Sabin.} -->
<!-- \label{tab:risk-categories} -->
<!-- \small -->
<!-- \end{table} -->

@@

```{r echo=FALSE, fig.cap="Surveys used in our analysis by year, survey type, sample size, and whether the survey included a transactional sex question."}
knitr::include_graphics("depends/available-surveys.pdf")
```

@@

```{r echo=FALSE, fig.cap="Percentage of new infections reached across all 13 countries, taking a variety of risk stratification approaches, against the percentage of at risk population reached."}
knitr::include_graphics("depends/infections-reached.pdf")
```

@@
